---
title: "CLT_WUP"
author: "Onalee Garusinghe"
output: 
  html_document:
    number_sections: true
    toc: true
    toc_depth: 5
date: "`r Sys.Date()`"    
    
---

kkardashtemp  see code below

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
require(tidyverse)
require(lattice)
```

```{r}
Homers_data <- read.csv(file="Homers_data.csv")

my1000 <- sample(Homers_data , size = 1000, replace=T)

```

```{r}

library(ggplot2)
sampleNumber = sample(1:10000, size = 1000)
library(dplyr)
my1000 <- Homers_data[sampleNumber, ]
names(my1000)
# Basic density
p <- ggplot(my1000, aes(x=kkardashtemp,col=sex)) + 
  geom_density()
p
# Add mean line
p+ geom_vline(aes(xintercept=mean(kkardashtemp)),
            color="blue", linetype="dashed", size=1)
print(paste('mean = ', mean(my1000$kkardashtemp),' sd = ',sd(my1000$kkardashtemp)))
```


```{r}
numb=36
Hdata = Homers_data[sample(1:1000, size=numb*1000, replace=T),"kkardashtemp"]
mdata  <-matrix(Hdata,nrow=1000,ncol=numb)
x.avg <- apply(mdata,1,mean)
my1000$k36 = x.avg

p <- ggplot(my1000, aes(x=k36)) + 
  geom_density() 
p

# Add mean line
  geom_vline(aes(xintercept=mean(k36)),
            color="blue", linetype="dashed", size=1)
print(paste('mean = ', mean(my1000$k36),' sd = ',sd(my1000$k36)))

```

    I believe with the numb being 36 and the sd being 6.730, I expect our new sd to be around 2.243. You can expect the new sd to be one third of the original.



```{r}
numb = 36
Hdata = Homers_data[sample(1:1000,size=numb*1000, replace=T),"kkardashtemp"]
mdata  <-matrix(Hdata,nrow=1000,ncol=numb)
x.avg <- apply(mdata,1,mean)
my1000$k36 = x.avg


p <- ggplot(my1000, aes(x=k36),col=sex) + 
  geom_density() +

# Add mean line
 geom_vline(aes(xintercept=mean(k36)),
            color="blue", linetype="dashed", size=1)
p + ggtitle("n = 25") +
  xlab("temperature") + ylab(" density")

print(paste('mean = ', mean(my1000$k36),' sd = ',sd(my1000$k36)))

```

  I believe with the numb being 36 and the original sd being 6.973, I expect the new sd to be 2.324. You can expect the new sd to be one third of the original.



  Unlike before the graph was more varied, this graph with our new standard deviation of about 7 with the numb 36, showing that the grahs have been smoother with each increase in numb, and the standard devuation have become smaller and smaller. The mean is about 49.58, so we can observe that the mean has stayed the same with each numb.
